### 2016-08-22 ms/ms.tex
modified discussion

Given that several changing points in network organization occured
during assembling, we next explored the species most likely
responsible for the observed shifts in interaciton patterns. Based on
a preferential attachment-like mechanism, we expect that the most
persistent and high degree species would remain stable in the network
core during assembly, and would thus contribute the least to the
changing points in network organization. Surprisingly however, we
encountered the opposite: the species that were most variable in their
network position and thus contributed most to network reorganizations
where species with the highest degrees (i.e., most generalized) and
persistence. For example, the five most ubiquitous species in our
study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
what module (i.e., community), and they were also present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources the intensively managed
agriculture landscape, and thus also most persistent. More persistent
species also have longer phenologies, so they have the opportunity to
visit many different flowers, resulting in a higher degree. Either
way, our result suggests that adaptable species can change their
network position to utilize the most advantageous floral resources
available, which my depend the other pollinator species that are
present and the state of the floral resource. Thus given the
opportunity and ability to use different resources, species will often
change their network positions.

>>>>

Given that several changing points in network organization occured
during assembly, we next explored the species most likely responsible
for the shifts in interaciton patterns. Based on a preferential
attachment-like mechanism, we expect that the most persistent and high
degree species would remain stable in the network core during
assembly, and would thus contribute the least to the changing points
in network organization. Surprisingly however, we encountered the
opposite: the species that were most variable in their network
position and thus contributed most to network reorganizations where
species with the highest degrees (i.e., most generalized) and
persistence. For example, the five most ubiquitous species in our
study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
what module (i.e., community), and they were also present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources the intensively managed
agriculture landscape, and thus also most persistent. More persistent
species also have longer phenologies, so they have the opportunity to
visit many different flowers, resulting in a higher degree. Either
way, our result suggests that adaptable species can change their
network position to utilize the most advantageous floral resources
available, which my depend the other pollinator species that are
present and the state of the floral resource. Thus given the
opportunity and ability to use different resources, species will often
change their network positions.
